The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
start editing section 4, and explain why we do not determine the LF directly in section 3.2

@@

\section{Results}
\label{S:results}
Having identified the overdense and underdense regions in a volume-limited sample (Sec.~\ref{sub:overdensities}, Sec.~\ref{sub:volumelimiting}), we will now see in this section if the morphological
parameters of the galaxies, listed in Sec.~\ref{sub:axisratio}, have any dependence on the environment that they reside in. We have 3 different ways of volume-limiting our sample
\begin{enumerate}
 \item no redshift evolution of luminosity cut $(\s1)$,
 \item use $B$-band evolution rate for $I$-band luminosities $(\s2)$,
 \item impose stellar mass cuts instead of luminosity $(\s3)$
\end{enumerate}
and we will present our results in each of the 3 cases.

>>>>

One might wonder why we cannot use the luminosity function in F814W
based on the COSMOS observations to directly determine the luminosity
function for our sample, thus simplifying this exercise.  However,
this turns out to be highly non-trivial for two reasons.  First, the
F814W observations are relatively shallow compared to the deep
ground-based observations used in many other works for determination
of luminosity evolution.  As a result, it is difficult to get a handle
on the faint end of the luminosity function, and the unknown faint-end
slope turns out to be degenerate with the evolution of the typical
luminosity.  Second, the photometric redshift error is a complicating
factor that requires sophisticated techniques to remove.  A derivation
of the $I$-band luminosity evolution is therefore beyond the scope of
this work.

@@

\section{Results}
\label{S:results}

Having identified the overdense and underdense regions in a
volume-limited sample (Secs.~\ref{sub:overdensities}
and~\ref{sub:volumelimiting}), we will now see whether the morphological
parameters of the galaxies described in Sec.~\ref{sub:axisratio}
depend noticably on the environment of the redshift slice in which
they reside. Note that for true 3D overdensities there is already
substantial evidence in the literature that we should see variation of
properties with the environment.  Our test is necessary to see
whether such morphology-density correlations are evident in the kind
of 1D redshift slices that would be used for constructing weak lensing
simulations, or whether our use of an area the size of COSMOS will
wash out these trends (which would be good news for weak lensing
simulations based on that dataset).

As described in Sec.~\ref{sub:volumelimiting}, we have three different ways of volume-limiting our sample:
\begin{enumerate}
 \item no redshift evolution of luminosity cut $(\s1)$,
 \item using $B$-band luminosity evolution applied to the $I$-band
   luminosities $(\s2)$, and
 \item impose stellar mass cuts instead of luminosity $(\s3)$.
\end{enumerate}

We will present our results in all three cases to check for their
robustness to how the sample is selected.
